%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{configuration}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-skyblue}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}
% \definecolor{sectiondivider}{HTML}{5D5D5D}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
% \photo[circle,noedge,left]{./profile}
\name{Eric Moses}{Ngigi}
\position{Software Developer{\enskip\cdotp\enskip}}
\address{Nairobi, Kenya}
\mobile{(+254) 725 682 601}
\email{ericmosesngigi@gmail.com}
%\dateofbirth{January 1st, 1970}
\homepage{ericngigi.netlify.app}
\github{erikngigi}
\linkedin{erik-ngigi}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \kaggle{kaggle-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra information}

% \quote{``Be the change that you want to see in the world."}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Iknal Semikan,}
  {Göteborg , Sweden.}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for Engineering Internship.}
% How the letter is opened
\letteropening{Dear Mr./Ms.}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
\letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal information
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[C]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Eric Moses Ngigi~~~·~~~Cover Letter}
  {}

% Print the title with above letter information
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

I am writing to apply for the internship position at Iknal Semikan as advertised on your website. Having recently completed my degree in Business Information Technology, a discipline of Computer Science, at Dedan Kimathi University of Technology, I am eager to apply my knowledge and skills in a practical setting within your esteemed organization.

Throughout my university education, I have developed a strong foundation in Computer Science, with a focus on Business Information Technology. This program has equipped me with a comprehensive understanding of programming languages, software development, database management, and IT project management. I am confident in my ability to leverage these skills to contribute to the diverse projects and challenges undertaken by Iknal Semikan.

In addition to my academic background, I possess the key competencies and qualities sought in the internship requirements. I have a solid understanding of languages such as C/C++ and Python, which I have utilized in various projects and coursework. I am adept at product-oriented design, algorithm development, and have a strong grasp of data structures and complexity analysis. These skills enable me to effectively approach and solve technical challenges.

As a creative thinker, I constantly seek innovative solutions and enjoy working collaboratively in team environments. I firmly believe in the power of effective communication and teamwork to achieve exceptional results. Throughout my academic journey, I actively participated in group projects, honing my ability to work well with diverse team members and effectively communicate complex ideas.

Moreover, I possess a strong work ethic and a self-driven nature. I am always eager to learn and expand my knowledge in the field of technology. I am confident in my ability to quickly adapt to new technologies, tools, and methodologies. As a proactive and motivated individual, I am committed to delivering high-quality work and exceeding expectations.

While English is not my native language, I am proficient in both written and verbal communication. I have consistently honed my English language skills throughout my studies and can confidently communicate ideas and collaborate effectively in an English-speaking environment.

I am genuinely excited about the opportunity to contribute to Iknal Semikan's projects and believe that my education, technical skills, and passion for technology make me an excellent fit for this internship position. I am confident that this experience will allow me to gain invaluable industry knowledge and further develop my professional skills.

I have attached my resume for your review, which provides further details about my qualifications and experiences. Thank you for considering my application. I am eager to discuss how my skills and enthusiasm align with your organization's goals during an interview. Please feel free to contact me at your convenience.

Thank you for your time and consideration.

\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter information
\makeletterclosing

\end{document}
