%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {DevOps Engineer} % Job title
    {Fiverr} % Organization
    {Freelance, Online} % Location
    {September 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Utilized GitHub Actions to automate the deployment process, enabling seamless and reliable deployments of web applications.}
        \item {Implemented Git version control and collaborated with the development team to ensure effective code management and streamlined collaboration.}
        \item {Developed and maintained web applications for various clients, resulting in a 30\% increase in user engagement and a 20\% boost in conversion rates.}
        \item {Designed and implemented CI/CD pipelines using Jenkins and Travis CI, reducing deployment time by 40\% and increasing development team productivity.}
        \item {Implemented Docker and Kubernetes for containerization, resulting in improved application performance and scalability.}
        \item {Reduced manual effort by 20\% through the scripting of routine tasks using Bash.}
        \item {Managed, configured and installed new firmware on new/existing firewalls/routers, managed switches, wireless access points and load balancers.}
        \item {Implemented robust security measures and maintained network configurations, ensuring compliance with industry standards and successfully passing all security audits.}
        \item {Worked with developers in development of the database schema design using the Entity-relationship model as per user requirements.}
        \item {Performed Database Performance Analysis and Tuning using Database Engine Tuning Advisor, SQL Server Profiler and SQL Server Extended Events.}
        \item {Collaborated with database administrators to optimize database performance, improving query response time by 35\% and enhancing overall application performance.}
        \item {Utilized cloud computing platforms such as AWS and Google Cloud Platform to deploy scalable infrastructure, reducing infrastructure costs by 30\% through efficient resource allocation and auto-scaling.}
        \item {Achieved 99.9\% server uptime in a cloud-based environment, resulting in increased system availability.}
        \item {Stayed updated with emerging technologies, industry trends, and best practices in web development, Linux system engineering, and cloud computing, leading to the successful adoption of new technologies and improved project outcomes.}
      \end{cvitems}
    }
%----------------------------------------------------------------------------------------------------------------------------
\cventry
    {Document Preparation} % Job title
    {SysCraft Limited} % Organization
    {Nairobi, Kenya} % Location
    {November 2022 - February 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Carefully handled private documents by sorting and or preparing hard copy records for scanning and document preparation.}
        \item {Followed production procedures in completing internal documentation and tracking.}
        \item {Adhered to imaging center guidelines of maintaining a clean work environment.}
        \item {Responsible for creating batches in the computer, scanning each batch, making sure the clarity of the documents is to client approval.}
        \item {Ability to work at a sustained pace to meet production rates while producing quality work.}
        \item {Possessed a strong problem solving ability, acceptable of change and long duration of project assignments.}
        \item {Ability to work independently with minimal supervision.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Data Analyst} % Job title
    {Nyeri Water and Sanitation Company} % Organization
    {Nyeri, Kenya} % Location
    {June 2019 - December 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed dashboards and reports using Tableau and Power BI, resulting in a 99\% increase in efficiency.}
        \item {Installing, configuring, and maintaining database management systems (DBMS) such as Oracle, MySQL, and SQL Server.}
        \item {Installed, administered and maintained MS SQL Server 2008/2012, including upgrades, security, configuration and service packs.}
        \item {Developed, documented and mantainied installation and configuration procedures on both Windows and Linux Environments.}
        \item {Build, installed and configured Red Hat Linux servers in a data center environment.}
        \item {Monitored performance and history of infastructure with tools such as CloudWatch and Datadog.}
        \item {Scheduled and automated full/differential/transactional backups and implemented recovery strategies.}
        \item {Created indexes (clustered and non-clustered) to speed up query performance resulting in a 99\% increase in efficiency.}
      \end{cvitems}
    }
% %---------------------------------------------------------
  % \cventry
  %   {Front-End Web Developer} % Job title
  %   {Kenya Scouts Association} % Organization
  %   {Nyeri, Kenya} % Location
  %   {} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of tasks/responsibilities
  %       \item {Developed in Cocos2d-x an action puzzle game(Dragon Buster) targeting U.S. market.}
  %       \item {Implemented API server which is communicating with game client and In-App Store, along with two other team members who wrote the game logic and designed game graphics.}
  %       \item {Won the 2nd prize in final evaluation.}
  %     \end{cvitems}
  %   }
  %
% %---------------------------------------------------------
%   \cventry
%     {Software Engineer} % Job title
%     {ShitOne Corp.} % Organization
%     {Seoul, S.Korea} % Location
%     {Dec. 2011 - Feb. 2012} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of tasks/responsibilities
%         \item {Developed a proxy drive smartphone application which connects proxy driver and customer.}
%         \item {Implemented overall Android application logic and wrote API server for community service, along with lead engineer who designed bidding protocol on raw socket and implemented API server for bidding.}
%       \end{cvitems}
%     }
%
% %---------------------------------------------------------
%   \cventry
%     {Freelance Penetration Tester} % Job title
%     {SAMSUNG Electronics} % Organization
%     {S.Korea} % Location
%     {Sep. 2013, Mar. 2011 - Oct. 2011} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of tasks/responsibilities
%         \item {Conducted penetration testing on SAMSUNG KNOX, which is solution for enterprise mobile security.}
%         \item {Conducted penetration testing on SAMSUNG Smart TV.}
%       \end{cvitems}
%       %\begin{cvsubentries}
%       %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
%       %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
%       %\end{cvsubentries}
%     }
%
%---------------------------------------------------------
\end{cventries}
